Supporting Information

### 2021-09-03 vertical-thermal-review_SI.Rmd
editing "the biophysical environment"
update table S2

@@

See [here](https://github.com/EcoClimLab/vertical-thermal-review/commit/3f624a119d72d388c707d21fb20666a2ad31848f#commitcomment-55784918) for rows to include.

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
parameters_table <- read.csv("NEON_height_profiles/HARV_neon_stats.csv", stringsAsFactors = FALSE, check.names = FALSE)
parameters_table <- parameters_table[c(9, 1, 3, 5)] #select and order columns for inclusion
ft <- flextable(parameters_table)
ft <- autofit(ft)
ft
```

>>>>

*be sure to cite @schimelNEONHierarchicallyDesigned2007.*

@@

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
parameters_table <- read.csv("NEON_height_profiles/HARV_neon_stats_handedit.csv", stringsAsFactors = FALSE, check.names = FALSE)
parameters_table <- parameters_table[which(parameters_table$include==1),c(9, 1, 3)] #select and order columns for inclusion
ft <- flextable(parameters_table)
ft <- autofit(ft)
ft
```
